This section outlines the customer requirements for the UR20 robotic arm to palletize uniform sized boxes. The project also includes the design and implementation of a custom robotic gripper that incorporates bellow suction cups to handle the boxes effectivelty. The robot arm will maintain full functionality in waiting for a box on the conveyor belt and locating it, picking it up and placing on a pallet. 
\subsection{Box Palletizing by UR20 Robot}
\subsubsection{Description}
The UR20 will be used to palletize boxes, process data, and stack boxes in an effective manner. The system will handle boxes of the same size, ensuring precise and efficient stacking.
\subsubsection{Source}
 CSE Senior Design project specifications
\subsubsection{Constraints}
Environment is suitable for operation of collaborative robot in a safe manner. 
\subsubsection{Standards}
ISO 10218-1 Robots and robotic devices — Safety requirements for industrial robots ensuring protective measures.
ISO 10218-2, Robots for industrial environments – Safety requirements to minimize hazards associated with robots and end effectors.
\subsubsection{Priority}
Critical
The priority of this requirement relative to other specified requirements. Use the following priorities:

\subsection{Custom Gripper with Vacuum and Bellow Cups}
\subsubsection{Description}
The gripper design will feature bellow cups and a vacuum to securely handle and move the boxes during the palletizing process. It will be designed to fit the size of the boxes and ensure firm grasping to prevent slippage during handling. The vacuum will be generated using an air compressor and an attachment along the tubing line that utilizes the Bernoulli principle.
\subsubsection{Source}
CSE Senior Design Project specifications
\subsubsection{Constraints}
The strength and durability of the bellow cups that support the box's weight, and the selection of materials on a limited budget.
\subsubsection{Standards}
ISO/TR 20218-1:2018 Robotics — Safety design for industrial robot systems, ensuring safety measures for design and integration of end-effectors.
ISO 10218-2, Robots for industrial environments – Safety requirements to minimize hazards associated with robots and end effectors.
\subsubsection{Priority}
High